Coupled response of stomatal and mesophyll conductance to light enhances photosynthesis of shade leaves under sunflecks

### 2016-07-06 gm_newphyt/manuscript_gmes.Rmd
minor edit on RH control
bad R2
text edit
last edits before manuscrupt submission

\
Courtney E. Campany^1^, Mark G. Tjoelker^1^, Susanne von Caemmere*R*^2^, Remko A. Duursma^1^.

@@

\
Author for Correspondence:
\
*Courtney Campany*
\
*Tel: +61(0)432391114*
\
*Email: courtneycampany@gmail.com*
\
\
Total word count (excluding summary, references and legends): 5563
\
Summary: 200
\
Introduction: 1186
\
Materials and Methods: 1863
\
Results: 1098
\
Discussion: 1380
\
Acknowledgements: 36
\
Number of figures: 7 (6 in color)
\
Number of tables: 2
\
Number of supporting information files: 4 figures, 1 methods

@@

# Summary
* Light gradients within tree canopies play a major role in the distribution of plant resources that define the photosynthetic capacity of sun and shade leaves. However, biochemical and diffusional constraints on gas exchange in sun and shade leaves in response to light remain poorly quantified, but critical for predicting carbon and water exchange in canopies.
* To investigate the CO~2~ diffusion pathway of sun and shade leaves, leaf gas exchange was coupled with  concurrent measurements of carbon isotope discrimination to measure net leaf photosynthesis (*A*~n~), stomatal conductance (*g*~s~) and mesophyll conductance (*g*~m~) in *Eucalyptus tereticornis* trees grown in the field in climate controlled whole tree chambers.
* Compared to sun leaves, shade leaves had lower *A*~n~, *g*~m~, leaf nitrogen and photosynthetic capacity (*V*~cmax~ and *J*~max~), but *g*~s~ was similar. When light intensity was temporarily increased for shade leaves to match that of sun leaves, both *g*~s~ and *g*~m~ increased, and *A*~n~ increased to values greater than sun leaves. 
* Here we show that dynamic physiological responses of shade leaves to altered light environments have implications for up-scaling leaf level measurements and predicting whole canopy carbon gain. Despite exhibiting reduced photosynthetic capacity, the rapid up-regulation of *g*~m~ with increased light enables shade leaves to respond quickly to sunflecks.

@@

\
Concurrent gas exchange and C isotope discrimination measurements were conducted based on methods described in Tazoe et al. [-@tazoe2011using] and Evans & von Caemmerer [-@evans2013temperature]. Leaf level gas exchange was measured with a standard (2 x 3 cm) leaf cuvette using a portable gas exchange system (LI-6400XT, LI-COR, Lincoln, NE, USA). This system was coupled with a tunable diode laser (TDL; TGA100,Campbell Scientific, Inc., Logan, UT, USA) for concurrent measurements of ^13^C isotope discrimination. The CO~2~ in the leaf cuvette was set at ambient atmospheric [CO~2~] (400 ppm) with a flow rate of 200 $\mu$mol s^-1^. Two identical gas exchange systems were run simultaneously, one in each of a randomly chosen WTC for each temperature treatment. Leaf temperatures were controlled at the current AT or ET WTC air temperature, and measurements were made at ambient air humidity. PPFD in the cuvette was set to match the individual light environment of each leaf type (explained above). Sustained periods of high irradiance (sunflecks) were simulated for shade leaves by increasing the leaf cuvette PPFD (LI-COR red/blue light source) to match the light environment of the sun leaf in the same tree. The maximum sunfleck response of shade leaves was then recorded once CO~2~ and water vapour fluxes re-stabilized in the leaf cuvette (ca. 25 min).

@@

```{r par, fig.width=7, fig.height=7, echo=FALSE,warning=FALSE,dev="png",message=FALSE, dpi=600, dev.args=list(type="cairo"), eval=includeFigs}
source("master_scripts/par2.R")
```  
\
**Figure 1**. Environmental conditions during the six measurement campaigns. Bars represent the local light environment for sun and shade leaves during six gas exchange campaigns from October 2013 to April 2014 (as photosynthetic photon flux density, PPFD). Means &pm; 1 standard error represent PPFD measured with a ceptometer at the height of each selected leaf in the canopy. Points connected by a line represent the mean (&pm; 1 standard error) daily maximum air temperature during each campaign period. Each date represents the starting date for each measurement campaign; each campaign was completed in 3 days.

\
```{r acicurves, fig.width=8, fig.height=10, warning=FALSE,echo=FALSE,dev="png", dpi=600,message=FALSE, dev.args=list(type="cairo"), eval=includeFigs}
 source("master_scripts/aci_vcmaxnitro.R")
```

>>>>

\
Courtney E. Campany^1^, Mark G. Tjoelker^1^, Susanne von Caemmerer^2^, Remko A. Duursma^1^.

@@

\
Author for Correspondence:
\
*Courtney Campany*
\
*Tel: +61(0)432391114*
\
*Email: courtneycampany@gmail.com*
\
\
Total word count (excluding summary, references and legends): 5903
\
Summary: 200
\
Introduction: 1242
\
Materials and Methods: 2106
\
Results: 1114
\
Discussion: 1393
\
Acknowledgements: 48
\
Number of figures: 7 (6 in color)
\
Number of tables: 2
\
Number of supporting information files: 4 figures, 1 methods

@@

# Summary
* Light gradients within tree canopies play a major role in the distribution of plant resources that define the photosynthetic capacity of sun and shade leaves. However, biochemical and diffusional constraints on gas exchange in sun and shade leaves in response to light remain poorly quantified, but critical for predicting canopy carbon and water exchange.
* To investigate the CO~2~ diffusion pathway of sun and shade leaves, leaf gas exchange was coupled with concurrent measurements of carbon isotope discrimination to measure net leaf photosynthesis (*A*~n~), stomatal conductance (*g*~s~) and mesophyll conductance (*g*~m~) in *Eucalyptus tereticornis* trees grown in climate controlled whole tree chambers.
* Compared to sun leaves, shade leaves had lower *A*~n~, *g*~m~, leaf nitrogen and photosynthetic capacity (*V*~cmax~ and *J*~max~), but *g*~s~ was similar. When light intensity was temporarily increased for shade leaves to match that of sun leaves, both *g*~s~ and *g*~m~ increased, and *A*~n~ increased to values greater than sun leaves. 
* Here we show that dynamic physiological responses of shade leaves to altered light environments have implications for up-scaling leaf level measurements and predicting whole canopy carbon gain. Despite exhibiting reduced photosynthetic capacity, the rapid up-regulation of *g*~m~ with increased light enables shade leaves to respond quickly to sunflecks.

@@

\
Concurrent gas exchange and C isotope discrimination measurements were conducted based on methods described in Tazoe et al. [-@tazoe2011using] and Evans & von Caemmerer [-@evans2013temperature]. Leaf level gas exchange was measured with a standard (2 x 3 cm) leaf cuvette using a portable gas exchange system (LI-6400XT, LI-COR, Lincoln, NE, USA). This system was coupled with a tunable diode laser (TDL; TGA100,Campbell Scientific, Inc., Logan, UT, USA) for concurrent measurements of ^13^C isotope discrimination. The CO~2~ in the leaf cuvette was set at ambient atmospheric [CO~2~] (400 ppm) with a flow rate of 200 $\mu$mol s^-1^. Two identical gas exchange systems were run simultaneously, one in each of a randomly chosen WTC for each temperature treatment. Leaf temperatures were controlled at the current AT or ET WTC air temperature, and measurements were made at ambient air humidity. Measurements were thus made across a range of air temperature and vapour pressure deficit (kPa) across the six campaigns. PPFD in the cuvette was set to match the individual light environment of each leaf type (explained above). Sustained periods of high irradiance (sunflecks) were simulated for shade leaves by increasing the leaf cuvette PPFD (LI-COR red/blue light source) to match the light environment of the sun leaf in the same tree. The maximum sunfleck response of shade leaves was then recorded once CO~2~ and water vapour fluxes re-stabilized in the leaf cuvette (ca. 25 min).

@@

```{r par, fig.width=7, fig.height=7, echo=FALSE,warning=FALSE,dev="png",message=FALSE, dpi=600, dev.args=list(type="cairo"), eval=includeFigs}
source("master_scripts/par2.R")
**Figure 1**. Environmental conditions during the six measurement campaigns. Bars represent the local light environment for sun and shade leaves during six gas exchange campaigns from October 2013 to April 2014 (as photosynthetic photon flux density, PPFD). Means &pm; 1 standard error represent PPFD measured with a ceptometer at the height of each selected leaf in the canopy. Points connected by a line represent the mean (&pm; 1 standard error) daily maximum air temperature during each campaign period. Each date represents the starting date for each measurement campaign; each campaign was completed in 3 days.
```{r acicurves, fig.width=8, fig.height=10, warning=FALSE,echo=FALSE,dev="png", dpi=600,message=FALSE, dev.args=list(type="cairo"), eval=includeFigs}
 source("master_scripts/aci_vcmaxnitro.R")
